Propositions as Sessions, Mechanically

### 2015-04-13 paper/formalisation.tex
Added forwards tactic example to Library reuse section.

\textbf{Library reuse.} One of the design goals of the development was to
reuse existing libraries wherever possible. Two such instances proved
extremely useful, first is the Metatheory library as already
mentioned. Second, is the library of tactics provided by the Software
Foundations online book~\cite{SF}.  The tactics helped in many ways including
simplifying introduction of assertions, providing convenient shorthands and
... Traditionally, assertions in Coq have to be explicitly written within a
proof leading to the use of empheremal names introduced by prover. If the
proof of the assertion follows from an already proved lemma and some
assumptions in the context this is unnecessary verbage and this is what the
library allows to omit \todo{example of using the forwards tactic} an example
of the so called forwards tactic is given below the $\sim$ is a a shorthand
for immediately applying \coqe$auto$ to all subgoals generated by the tactic.

>>>>

\textbf{Library reuse.} One of the design goals of the development was to
reuse existing libraries wherever possible. Two such instances proved
extremely useful, first is the Metatheory library as already
mentioned. Second, is the library of tactics provided by the Software
Foundations online book~\cite{SF}. The tactics helped in many ways including
simplifying the introduction of assertions and providing convenient shorthands
for commonly executed sequences of tactics. An example for simplifying
assertions would be the \coqe!forwards! tactic permitting lemma
instantiation. Consider the following example (during the proof of $assoc_1$):
\begin{tabular}{l}
\begin{coq}
1 subgoal
(* ... other elements of the proof context ... *)
PER : Permutation (x $\sim$ B ++ $\GD$P) ($\GD$P0++$\GD$Q0)
UN : uniq (x $\sim$ B ++ $\GD$P)
\end{coq}\\ \hline
\begin{coq}
$\nu$ A.(P $\mid$ $\nu$ B.($\open{0}{1}{Q}$ $\mid$ R)) $\tpcp$ $\Gamma$
\end{coq}
\end{tabular}
\\~\\

In order to proceed with proving the goal, it is necessary to show that
$\GD$P0++$\GD$Q0 is unique. The proof follows from \key{PER} and \key{UN} upon
application of an appropriate lemma, and there are two possible ways to prove
this using plain Coq. One way is to apply the lemma to one of \key{PER} and
\key{UN} thereby replacing the chosen hypothesis with the conclusion of the
lemma (termed \textit{forward reasoning}). The opposite of forward reasoning,
namely backward reasoning, does not apply since the goal has nothing to do
uniqueness of $\GD$P0++$\GD$Q0. However, using the \coqe!assert! tactic one
can utilise backward reasoning. An assertion temporarily focuses a different
goal (the asserted goal) which may then be tackled using tactics in the
standard way. Unfortunately, this approach requires the explicit writing of
the goal, namely \coqe!uniq ($\GD$P0++$\GD$Q0)!, into the proof script of the
lemma cluttering the proof script sensitive to change because \coqe!$\GD$P0!
and \coqe!$\GD$Q0! are emphemeral names introduced by prover.

The \coqe!forwards! tactic avoids the problem of explicit names by allowing
the uniqueness property to be proven succiently:
\begin{coq}
forwards UN1: uniq_perm PER UN.
\end{coq}

where \coqe!uniq_perm! is the appropriate lemma and \coqe!UN1! is the name
given to the desired uniqueness property. Note that \key{PER} and \key{UN} are
mentioned in the proof with \coqe!assert! so the use of \coqe!forwards! has
reduced the dependencies on introduced names. The improvement is more
pronounced in cases where the goal is particularly long involving many
variables from the context.
